Ice sheet mass flows

### 2024-06-04 sankey.tex
labels (commented)
Comment out labels
Drawdown is not split by components (FRET, GZRET)

    \ifthenelse{\Q{MG} < \Q{ML}}
      {
        %% mass loss
        \sankeynode{name=fML, quantity=\Q{ML}, at={[xshift=\xoff]SF.left}, anchor=right}
        \sankeystart[red]{fML}
        \sankeyadvance[red-to-ice]{fML}{5mm}
        \sankeyfork{fML}{\Q{FRET}/f18, \Q{GZRET}/f17, \Q{MLfd}/f16}
        \sankeyadvance{f16}{10mm}

        \sankeynode{name=f17a, quantity=\qq{f17},
          at={[xshift=\xoff]f16.left}, anchor=right}
        \sankeyoutin{f17}{f17a}

        \sankeynode{name=f18a, quantity=\qq{f18},
          at={[xshift=\xoff]f17a.left}, anchor=right}
        \sankeyoutin{f18}{f18a}

        \sankeynode{name=f19, quantity=\qq{ML-in},
          at={ML-in.center}, anchor=center,
          forked={\qq{f18}/f18b, \qq{f17}/f17b, \qq{f16}/f16b}}
        \sankeyoutin{f16}{f16b}
        \sankeyoutin{f17a}{f17b}
        \sankeyoutin{f18a}{f18b}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{fMGa}{3mm}
        \sankeyend[black]{fMGa}
      }

@@

  %%   \node[anchor=south east, align=center, shift=({2mm,-3mm})] at (EV-out.right) {Evaporation\\(\Q{EV})};

  %%   \node[anchor=east, align=center, shift=({0mm,-1cm})] at (RU-NET.center) {Net Runoff\\(\sankeygetnodeqty{RU-NET})};

  %%   \node[anchor=center, align=center, shift=({0mm,-1cm})] at (SUB.center) {Submarine\\melt \\(\sankeygetnodeqty{SUB})};

  %%   \node[anchor=center, align=center, shift=({0mm,-1cm})] at (ICE.center) {Calving\\(\sankeygetnodeqty{ICE})};

  %%   \node[anchor=north, align=center, rotate=0, shift=({0cm, -0.5cm})] at (BM.center) {Basal\\melting \\(\sankeygetnodeqty{BM})};

  %%   \node[anchor=center, align=center, shift=({0mm,0cm})] at (DYN.center) {Dynamics\\(\sankeygetnodeqty{DYN})};

  %%   \node[anchor=center, align=center, shift=({-0.6cm,2cm})] at (RU-from-MELT.center) {Melt\\ runoff\\(\sankeygetnodeqty{RU-from-MELT})};

  %%   \node[anchor=center, align=right, shift=({-1cm,-1cm})] at (GROSS-to-MELT.center) {Melting \\(\sankeygetnodeqty{GROSS-to-MELT})};

  %%   \node[anchor=right, align=right, shift=({-2cm,1cm})] at (RFZ-from-MELT.center) {Refreezing\\loop \\(\sankeygetnodeqty{RFZ-from-MELT})};

  %%   \node[anchor=center, align=center, shift=({0.2cm,1cm})] at (SU-out.center) {Sublimation\\(\sankeygetnodeqty{SU-out})};

  %%   \node[anchor=center, align=center, shift=({1cm,0.1cm})] at (MGNet-out.center) {Net mass gain\\(\sankeygetnodeqty{MGNet-out})};

  %%   \node[anchor=north, align=center, rotate=0, shift=({0cm, 0.0cm})] at (FRET.center) {Frontal retreat \\(\sankeygetnodeqty{FRET})};

  %%   \node[anchor=north, align=center, rotate=0, shift=({0cm, 0.0cm})] at (GZRET-DYN.center) {Grounding line retreat \\(\sankeygetnodeqty{GZRET-DYN})};

  %% \node[anchor=center, align=center, shift=({0cm,0.75cm})] at (SF.center) {Snowfall (\sankeygetnodeqty{SF})};

  %%   \node[anchor=east, align=center, rotate=0, shift=({-0mm,0.2cm})] at (DP.center) {Deposition (\sankeygetnodeqty{DP})};

  %%   \node[anchor=east, align=center, rotate=0, shift=({-0mm,0.2cm})] at (CD.center) {Condensation (\sankeygetnodeqty{CD})};

  %%   \node[anchor=east, align=center, rotate=0, shift=({-0mm,0.3cm})] at (RF-NET.center) {Net rainfall (\sankeygetnodeqty{RF-NET})};

>>>>

    \ifthenelse{\Q{MG} < \Q{ML}}
      {
        %% mass loss
        \sankeynode{name=fML, quantity=\Q{ML}, at={[xshift=\xoff,yshift=0mm]SF.left}, anchor=right}%, angle=-145}
        \sankeystart[red]{fML}
        \sankeyadvance[red-to-ice]{fML}{5mm}
        \sankeyoutin{fML}{ML-in}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{fMGa}{3mm}
        \sankeyend[black]{fMGa}
      }

@@

      %% \foreach \mag in {SF,f0,RFZ-in,f6,fRU,fSUBa,fD,fGZa,fFRa,fSUa2,fEVa} {
      %%   \node at (\mag.center) {\qq{\mag}};
      %% }

      %% \ifthenelse{\Q{MG} < \Q{ML}} {
      %%   \node at (fML.center) {\qq{fML}};
      %% } {
      %%   \node at (fMGa.center) {\qq{fMGa}};
      %% }
